Variable Selection

### 2015-07-02 var_select.rmd
finished var_select

#change unknown Num.disc to be 1
all7b[is.na(all7b$Num.disc),]$Num.disc <- 1
# write.csv(all7b,'all7b.csv')

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)
write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

#Billing.Type - 'Estimate' and 'FeeProposal' and 'NoCharge' should be NA
all7c[all7c$Billing.Type %in% c('Estimate','FeeProposal','NoCharge'),]$Billing.Type<- NA

@@

mini.core3 <- all7c %>%
        select(Discipline , inv.mlsto , Business, client.count,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, pc.director,
        pc.pro , code.director , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

@@

* ProjEng.Pos
* code.ProjEng
* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Secondary
* Job.Type.Primary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

@@

#overlapping NA values for variables with many NA's
# first lets look at Job.Detail.Secondary, Job.Type.Primary, Type, JD.Primary, JD.Second
experiment<- all7c
experiment<- experiment %>% select(code.client, Post.Code, Billing.Type, Job.Source, Job.Detail.Secondary, Job.Type.Primary, Type, Project.Value,
                                   no.employees, client.age, contact.count, JD.Primary, JD.Second, dist, code.contact, client.age)
experiment<- sapply(experiment, function(x) is.na(x))
NA.plot<- melt(experiment)
NA.plot$mlsto<- rep(all7c$mlsto, ncol(experiment))
#reorder levels for ggplot by total number of NA TRUE
# table(NA.plot$Var2, NA.plot$value)[,'TRUE']
NA.plot <- within(NA.plot, 
                         Var2 <- factor(Var2, 
                                               levels=names(sort(table(NA.plot$Var2, NA.plot$value)[,'TRUE'], 
                                                                 decreasing=FALSE))))

@@

* dist and Post.Code
* Job.Type.Primary and JD.Primary
* code.contact and contact.count

@@

vars<- list('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', c('dist','Post.Code'),
            c('code.contact','contact.count'), c('Job.Type.Primary','JD.Primary'))
cfor.plotsave<- function(extra= vars, name= 'vara'){
        for(i in 1:length(vars)){

                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'client.numinv','pc.director', 'code.director', 'Num.disc', 
                        'Business', 'Biz.type', 'return.pdol', extra[[i]])]
                core.var = core.var[!is.na(core.var[,extra[[i]][1]]),]

@@

cfor.plotsave(extra=vars, name='vara')
cfor.plotsave(extra=vars, name='varb')

@@

* code.contact - ranks 2nd after timespan/2nd
* code.client (ranks 4th/4th)
* Project.Value (ranks 3rd/4th)
* no.employees - ranks 7th - before code.director  / 3rd last 
* JD.Second - ranks 6th - before code.director and Num.disc / 5th
* Billing.Type - ranks 3rd last but I can't see how this is not important/last
* Job.Type.Primary - ranks 7th - 6 nice broad categories/4th last

Throwing out:
* Job.Source - ranked last / 3rd last
* Job.Detail.Secondary - too patchy I believe / 3rd last
* Type - nice and broad but didn't seem to work - ranked 4th last / 2nd last
* client.age - 3rd last/last
* contact.count - 4th last/3rd last
* dist - 5th last/last
* Post.Code - 6th last or 7th last 
* contact.count - 3rd last/4th last 
* JD.Primary - 3rd last :(/2nd last

```{r run anova on all, echo=FALSE}
vars.vec<- c('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', 'dist','Post.Code',
            'code.contact','contact.count', 'Job.Type.Primary','JD.Primary')

aov.loop<- function(extra=vars.vec){
        for (i in 1:length(extra)){
                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'client.numinv','pc.director', 'code.director', 'Num.disc', 
                        'Business', 'Biz.type', 'return.pdol', extra[i])]
                core.var = core.var[!is.na(core.var[,extra[i]]),]

                formula = paste("return.pdol ~ inv.mlsto + Discipline + Business+
                        Biz.type + Num.disc +
                        no.users + client.numinv +
                        pc.director + client.totinv + 
                        pc.pro + timespan +
                        code.director +", extra[i], sep="+")

@@

                assign(paste("summ.",extra[i],sep=""), model, envir=.GlobalEnv)

@@

@@

* Project.Value - 17%
* Post.Code - 11.4%
* code.contact - .000013%

@@

```{r Tukey Ancova visualisation, echo=FALSE}

all.vars<- colnames(all7c %>% select(-mlsto))

auto.BP<- function(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='box'){

@@

                r= ggplot(df[!is.na(df[,colnames[i]]),],
                       aes_string(x=colnames[i], y=yvar, colour = colnames[i])) + 
                        geom_boxplot(alpha = 0, size = .2, outlier.size = .5)+
                        geom_jitter(alpha= 0.5, size=.2) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =9.5),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 1, size = .5)

@@

auto.BP(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='box')

@@

colnames(all7c)

>>>>

#change unknown Num.disc to be 1
all7b[is.na(all7b$Num.disc),]$Num.disc <- 1

#create new variable - tech.pos
all7b %>% select(pc.contracttech, pc.midtech, pc.seniortech) %>% slice(1000:1020)
test<- melt(all7b %>% select(mlsto, pc.contracttech, pc.midtech, pc.seniortech))
test<- ddply(test, .(mlsto), max= max(value))
#delete any rows where percentage is less than 10
test<- test[!test$value<10,] %>% arrange(mlsto,-value)
#now I just want the first row for every milestone - ie tech person that did the MOST
test2<- ddply(test, .(mlsto), function(x) head(x,1))
#now delete pc from the front of all the variables
test2$variable<- sapply(test2$variable,FUN=function(x){
        substr(x,4,15)})
test2$variable<- as.factor(test2$variable)
test2$value.bin<- cut(test2$value,9)
table(test2$variable, test2$value.bin)
mosaicplot(test2$variable ~ test2$value.bin, color=brewer.pal(9,"Spectral"),
           cex.axis = .5)
all7b<- merge(all7b, test2 %>% select(mlsto, variable), by='mlsto', all.x=TRUE, all.y=FALSE)
colnames(all7b)[names(all7b) %in% 'variable']<-'pos.tech'

#create new variable - majority.pos
all7b %>% select(pc.contracttech, pc.midtech, pc.seniortech, pc.director, pc.seniorpro, pc.midpro) %>% slice(1000:1020)
testa<- melt(all7b %>% select(mlsto, pc.contracttech, pc.midtech, pc.seniortech, pc.director, pc.gradpro,
                             pc.midpro, pc.seniorpro, pc.unknown))
#delete any rows where percentage is less than 10
testa<- testa[!testa$value<10,] %>% arrange(mlsto,-value)
#now I just want the first row for every milestone - ie tech person that did the MOST
testa2<- ddply(testa, .(mlsto), function(x) head(x,1))
#now delete pc from the front of all the variables
testa2$variable<- sapply(testa2$variable,FUN=function(x){
        substr(x,4,15)})
testa2$variable<- as.factor(testa2$variable)
#create bins for mosaic plot
testa2$value.bin<- cut(testa2$value,5)
table(testa2$variable, testa2$value.bin)
#reorder levels for mosaic plot
testa2$variable <- factor(testa2$variable, levels=names(sort(table(testa2$variable), 
                                                                 decreasing=TRUE)))
mosaicplot(testa2$variable ~ testa2$value.bin, color=brewer.pal(9,"Spectral"),
           cex.axis = .6)
all7b<- merge(all7b, testa2 %>% select(mlsto, variable), by='mlsto', all.x=TRUE, all.y=FALSE)
colnames(all7b)[names(all7b) %in% 'variable']<-'majority.pos'
all7b[all7b$majority.pos %in% 'unknown',]$majority.pos<- NA

# write.csv(all7b,'all7b.csv')

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)
# write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

#Billing.Type - 'Estimate' and 'FeeProposal' and 'NoCharge' should be NA
all7c[all7c$Billing.Type %in% c('Estimate','FeeProposal','No Charge'),]$Billing.Type<- NA

@@

mini.core3 <- all7c %>%
        select(Discipline , inv.mlsto , Business, client.count,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol,
        pc.pro , code.director , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

@@

* ProjEng.Pos
* code.ProjEng
* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Secondary
* Job.Type.Primary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age
* majority.pos

@@

#overlapping NA values for variables with many NA's
# first lets look at Job.Detail.Secondary, Job.Type.Primary, Type, JD.Primary, JD.Second
experiment<- all7c
experiment<- experiment %>% select(code.client, Post.Code, Billing.Type, Job.Source, Job.Detail.Secondary, 
                                   Job.Type.Primary, Type, Project.Value,
                                   no.employees, client.age, contact.count, JD.Primary, JD.Second, dist, code.contact,
                                   client.age, ProjEng.Pos, code.ProjEng, majority.pos )
experiment<- sapply(experiment, function(x) is.na(x))
NA.plot<- melt(experiment)
NA.plot$mlsto<- rep(all7c$mlsto, ncol(experiment))
#reorder levels for ggplot by total number of NA TRUE
# table(NA.plot$Var2, NA.plot$value)[,'TRUE']
NA.plot <- within(NA.plot, 
                         Var2 <- factor(Var2, 
                                               levels=names(sort(table(NA.plot$Var2, NA.plot$value)[,'TRUE'], 
                                                                 decreasing=FALSE))))

@@

* dist and Post.Code
* Job.Type.Primary and JD.Primary
* code.contact and contact.count
* ProjEng.Pos and code.ProjEng

@@

vars<- list('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', 'pos.tech', 'majority.pos',
            c('dist','Post.Code'),
            c('code.contact','contact.count'), c('Job.Type.Primary','JD.Primary'),
            c('ProjEng.Pos', 'code.ProjEng'))

cfor.plotsave<- function(extra= vars, name= 'vare'){
        for(i in 1:length(vars)){

                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'pc.director', 'code.director', 'Num.disc', 
                        'Business', 'Biz.type', 'Biz.size', 'return.pdol', extra[[i]])]
                core.var = core.var[!is.na(core.var[,extra[[i]][1]]),]

@@

cfor.plotsave(extra=vars, name='vara')
cfor.plotsave(extra=vars, name='varb')
cfor.plotsave(extra=vars, name='varc')
cfor.plotsave(extra=vars, name='vard')
cfor.plotsave(extra=list('majority.pos'), name='vare')

@@

* code.contact - ranks 4th after no.users, timespan, pc.pro
* code.client (ranks 4th/4th)
* Project.Value (ranks 4th/5th)
* JD.Second - ranks 6/6th - before code.director and Num.disc / 5th
* Billing.Type - ranks 3rd last/4th last but I can't see how this is not important/last
* Post.Code - 4th
* code.ProjEng - 8th
* majority.pos

Throwing out:
* Job.Source - ranked 4th last/3rd last
* Job.Detail.Secondary - too patchy I believe / 5th last/3rd last
* Type - nice and broad but didn't seem to work - ranked 5th last / 3rd last
* client.age - last/last
* contact.count - 4th last/last
* dist - 3rd last/2nd last
* Post.Code - 6th last or 7th last 
* contact.count - last/2nd lsat 
* ProjEng.Pos - 3rd last/ 4th last
* no.employees - 3rd last / 2nd last
* Job.Type.Primary - 3rd last
* JD.Primary - 8th/9th,ie 7th last not too bad - too similar to JD.Second and JD.Second performs better

```{r run anova on all, echo=FALSE}
vars.vec<- c('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', 'dist','Post.Code',
            'code.contact','contact.count', 'Job.Type.Primary','JD.Primary','ProjEng.Pos', 'code.ProjEng', 'pos.tech',
            'majority.pos')

aov.loop<- function(extra=vars.vec){
        for (i in 1:length(extra)){
                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'Biz.type','code.director', 'Num.disc', 
                        'Business', 'return.pdol', extra[i])]
                core.var = core.var[!is.na(core.var[,extra[i]]),]

                formula = paste("return.pdol ~ inv.mlsto + Discipline + Business+
                        Biz.type + Num.disc +
                        no.users + 
                        client.totinv + 
                        pc.pro + timespan +
                        code.director", extra[i], sep="+")

@@

                print(extra[i])
                print(model %>% summary)

@@

#try adding pc.director and pc.seniorpro to make pc.seniorpro.d - didn't go that well

# all7c<- transform(all7c, pc.seniorpro.d = pc.seniorpro+pc.director)

@@

* Project.Value - 17%
* Post.Code - 23%
* code.contact - 14.4%
* code.client - .25%
* JD.Second - 1.25%
* dist - 17%
* JD.Primary - 9.8% - delete, confusing with JD.Second
* ProjEng.Pos - 1.5%
* code.ProjEng - .9%
* majority.pos - 3.7%

@@

```{r boxplots of each variable, echo=FALSE}

auto.BP<- function(yvar = 'return.pdol', df= all7c, name='box'){

        colnames= colnames(df %>% select(-mlsto))

@@

                r= ggplot(df[!is.na(df[,colnames[i]]),],
                       aes_string(x=colnames[i], y=yvar, colour = colnames[i])) + 
                        geom_boxplot(alpha = 0, size = .5, outlier.size = .5)+
                        geom_jitter(alpha= 0.5, size=.5) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =9.5),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 1, size = .6)

@@

auto.BP(yvar = 'return.pdol', df= all7c %>% select(mlsto,return.pdol, majority.pos), name='box_maj')

@@

Visualise all numerical variables as boxplots vs return.pdol

```{r boxplots numeric vars, echo=FALSE}

autonum.BP<- function(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='box', breaks=4){

                #only perform plot if variable is a factor
                #if variable is numeric or an integer, break into 8 bins

                #how many total cols
                        tot.num = df %>% ncol
                        #how many numeric variables?
                        num = df[,!sapply(df, is.factor)] %>% ncol

                if(df[,colnames[i]] %>% class %in% c('numeric', 'integer')) {
#                         print('yes')}

                        #cut numeric columns into new variables with 8 categories, these are called 'cuti' 
                        df[, paste0('cut',i)] <- cut_number(df[,colnames[i]] %>% as.numeric, breaks)
#                         df[, paste0('cut',i)] <- cut_number(df[,colnames[i]] %>% as.numeric, 8)

#                 medians= ddply(df,
#                                .(df[,paste0('cut',i)]), summarise, med=median(return.pdol))

#                 df[,paste0('cut',i)] <- factor(df[,paste0('cut',i)], 
#                                                levels= medians[order(-medians$med),][,1] )

                r= ggplot(df[!is.na(df[,paste0('cut',i)]),],
                       aes_string(x=paste0('cut',i), y=yvar, colour = paste0('cut',i))) + 
                        geom_boxplot(alpha = 0, size = .8, outlier.size = 1)+
                        geom_jitter(alpha= 0.4, size=1) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =12),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 2, size = 1)

df<- all7c %>% select(-X, -No.Blue.Files, -contact.count, -no.users, -pc.contracttech,
                      -pc.director, -pc.gradpro, -pc.midpro, -pc.midtech,-pc.seniorpro, -pc.seniortech,
                      -pc.unknown, -pc.pro, -pc.tech, -Year, -Num.disc, -mean.peeps,
                      -dis.sc.mlsto, -num.inv, -num.neginv, -client.neginv, -client.count)
all.vars<- colnames(df)
autonum.BP(colnames=all.vars, yvar = 'return.pdol', df= df, name='boxnum', breaks=8)

Visualise all percent variables, cut into 5, ie 0-20%, 20-40% etc

```{r boxplots numeric vars, echo=FALSE}

autopc.BP<- function(colnames=all.vars, yvar = 'return.pdol', df= df1, name='box', breaks=5){

                #how many total cols
                        tot.num = df %>% ncol
                        #how many numeric variables?
                        num = df[,!sapply(df, is.factor)] %>% ncol

                if(df[,colnames[i]] %>% class %in% c('numeric', 'integer')) {
#                         print('yes')}

                        #remove rows which =0
                        df2<- df[!(df[,colnames[i]] == 0),]
                        #cut numeric columns into new variables with 8 categories, these are called 'cuti' 
                        df2[, paste0('cut',i)] <- cut(df2[,colnames[i]] %>% as.numeric, breaks)
#                         df[, paste0('cut',i)] <- cut_number(df[,colnames[i]] %>% as.numeric, 8)

#                 medians= ddply(df,
#                                .(df[,paste0('cut',i)]), summarise, med=median(return.pdol))

#                 df[,paste0('cut',i)] <- factor(df[,paste0('cut',i)], 
#                                                levels= medians[order(-medians$med),][,1] )

                r= ggplot(df2[!is.na(df2[,paste0('cut',i)]),],
                       aes_string(x=paste0('cut',i), y=yvar, colour = paste0('cut',i))) + 
                        geom_boxplot(alpha = 0, size = .8, outlier.size = 1)+
                        geom_jitter(alpha= 0.4, size=1) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =12),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 2, size = 1)

df1<- all7c %>% select(pc.contracttech, return.pdol,
                      pc.director, pc.gradpro, pc.midpro, pc.midtech,pc.seniorpro, pc.seniortech,
                      pc.unknown, pc.pro, pc.tech, Year, mean.peeps, dis.sc.mlsto)
all.vars<- colnames(df1)
autopc.BP(colnames=all.vars, yvar = 'return.pdol', df= df1, name='boxpc', breaks=5)

#test - added pc.seniorpro and pc.director together - didn't go that well
# trial<- c('pc.seniorpro.d')
# autopc.BP(colnames=trial, yvar = 'return.pdol', df= all7c %>% select(return.pdol,pc.seniorpro.d), name='boxpca', 
#           breaks=5)

Plot integers which don't need cutting

autoint.BP<- function(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='boxint'){

        for (i in 2:length(colnames)){

                df[,colnames[i]]<- as.factor(df[,colnames[i]])

                r= ggplot(df[!is.na(df[,colnames[i]]),],
                       aes_string(x=colnames[i], y= yvar, colour = colnames[i] )) + 
                        geom_boxplot(alpha = 0, size = .8, outlier.size = 1)+
                        geom_jitter(alpha= 0.4, size=1) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =12),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 2, size = 1)

df<- all7c %>% select(return.pdol, No.Blue.Files, contact.count, no.users, Num.disc,
                      num.inv, num.neginv, client.neginv, client.count)
all.vars<- colnames(df)
autoint.BP(colnames=all.vars, yvar = 'return.pdol', df= df, name='boxint')
